\section{Experiments}
\label{secExperiments}

\subsection{Datasets}
\textbf{WIDER FACE dataset.}
One of the most popular dataset to benchmark the face detection models is WIDER FACE dataset \cite{yang2016wider}.
The dataset contains 32,203 images with 393,703 face bounding boxes.
Face bounding boxes in WIDER FACE dataset are in various scales, poses, expressions, occlusions and illuminations.
The WIDER FACE dataset is split into three subsets: training (40\%), validation (10\%) and testing (50\%) with three level of difficulty: Easy, Medium and Hard based on the detection rate of EdgeBox \cite{zitnick2014edge}.
Moreover, five facial landmarks annotation was added into the training and validation subset of WIDER FACE by \cite{deng2020retinaface}.

\textbf{WIDER FACE 4K validation subset.}
In order to benchmark the performance of face detection solutions while working with high resolution images, we propose an extra validation subset of WIDER FACE dataset.
This subset consists of images which was made by concatenating multiple images from original WIDER FACE validation subset.

\subsection{Implementation details}
\textbf{Detection branch.}

\textbf{Focus branch.}

\textbf{Data augmentation.}

\textbf{Training configs.} We use ... optimizer with .... to train our RetinaFocus.
The learning rate scheduler starts from ...., ....., .....
It takes ... days to finish the whole ... epoch training process on two NVIDIA RTX 2080Ti (12Gb) GPUs.

\textbf{Inference configs.}

\subsection{Ablation Study}
\textbf{Parameters for Focus Pixel.}

\textbf{FPN feature maps for Focus branch.}

\subsection{Face detection accuracy and speed trade-off}
\textbf{.}